Predicting the transmission of COVID-19 using inter and intra-county mobility: a mathematical modelling study

### 2022-12-28 Manuscripts/main.tex
too lazy to write
Update new files.
Tuning the model, bug fixes.
Update

\usepackage[utf8]{inputenc}
\usepackage{lineno}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{calrsfs}
\usepackage{pgfplots}
\usepackage[affil-it]{authblk}
\usepackage{color}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{cancel}
\usepackage{manyfoot}
\usepackage[margin=2.5cm]{geometry}
\usepackage{hyperref}
\usepackage{tcolorbox}
\usepackage[english]{babel}
\usepackage{amsthm}
\usepackage{soul}

@@

\mainfigure Essentially, the model takes in
\begin{enumerate}
    \item \important{PAST} Time-series data of the no. cases in Ontario in 26 PHUs
    \item \important{PAST} Time-series data of the ratio of 1st, 2nd, and 3rd dose vaccination in Ontario
    \item Labour force data and the commute matrix in Ontario
    \item Contact Matrix and CoMix
    \item \important{PREDICTED} Google mobility data in Ontario \emphasize{(Generated from NN)}
    \item Epidemiological parameters
    \item Vaccine parameters and time-series data of the \important{PREDICTED} immunity waning effects
    \item Whether we use machine learning to address the
\end{enumerate}
and outputs
\begin{itemize}
    \item no. cases in each district
    \item no. severe cases (ICU occupancy) in each district
    \item no. deaths in each district
\end{itemize}

@@

\begin{center}
    \begin{table}[h]
    \caption{Convolutional kernels in the model as probability distributions}
    \centering
\begin{tabular}[H]{p{2cm}p{6cm}p{4cm}p{3cm}}
     \textbf{Parameter}& \textbf{Description}  & \textbf{Value}& \textbf{Reference} \\
     \midrule
     $d_E$ & Latent period ($E$ to $I_p$ and $E$ to $I_s$) & $\sim gamma(2.5,4)$ & Davies et al.\\
     $d_c$ & Duration of clinical infectiousness& $\sim gamma(2.5,4)$ &  Davies et al.\\
     $d_s$ & Duration of sub-clinical infectiousness& $\sim gamma(5,4)$ &  Davies et al.\\
     $d_{pos}$ & Duration of PCR positivity& $\sim normal(9.87, 0.25)$ & [REF]\\ 
     $d_{hosp}$ & Duration from PCR positivity to hospitalization& $\sim normal(7.5, 1)$ & Davies et al.\\ 
     $d_{ICU}$ & Duration from hospitalization to ICU& $\sim normal(3.6, 1)$ & Davies et al.\\ 
     $d_{R,hosp}$ & Average stay in hospital & $\sim normal(11.08, 1.2)$ & Davies et al.\\ 
     $d_{R,ICU}$ & Average stay in hospital & $\sim normal(13.33, 1.2)$ & Davies et al.
    \end{tabular}
\end{table}
\end{center}

>>>>

\usepackage[utf8]{inputenc}
\usepackage{lineno}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{calrsfs}
\usepackage{pgfplots}
\usepackage[affil-it]{authblk}
\usepackage{color}
\usepackage{svg}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{cancel}
\usepackage{manyfoot}
\usepackage[margin=2.5cm]{geometry}
\usepackage{hyperref}
\usepackage{tcolorbox}
\usepackage[english]{babel}
\usepackage{amsthm}
\usepackage{soul}

@@

\section{Supplementary analysis}

\begin{figure}[h]
    \includegraphics*[width=\textwidth]{vaccine_unvaccinated.jpg}
    \includegraphics*[width=\textwidth]{vaccine_vaccined.jpg}
    \textbf{Figure S1:} Relative effectiveness of natural, vaccine, and hybrid immunity.
\end{figure}

\begin{figure}[h]
    \includegraphics*[width=\textwidth]{Three_paper_avg.jpg}
    \textbf{Figure S1:} Estimating the effectiveness of 2 and 3 doses of vaccination against clinical infection of the omicron variant of SARS-Cov-2.
\end{figure}

@@

\begin{center}
    \begin{table}[h]
    \caption{Epidemiological convolutional kernels in the model as probability distributions}
    \centering
\begin{tabular}[H]{p{2cm}p{6cm}p{4cm}p{3cm}}
     \textbf{Parameter}& \textbf{Description}  & \textbf{Value}& \textbf{Reference} \\
     \midrule
     $d_E$ & Latent period ($E$ to $I_p$ and $E$ to $I_s$) & $\sim gamma(2.5,4)$ & Davies et al.\\
     $d_c$ & Duration of clinical infectiousness& $\sim gamma(2.5,4)$ &  Davies et al.\\
     $d_s$ & Duration of sub-clinical infectiousness& $\sim gamma(5,4)$ &  Davies et al.\\
     $d_{pos}$ & Duration of PCR positivity& $\sim normal(9.87, 0.25)$ & [REF]\\ 
     $d_{hosp}$ & Duration from PCR positivity to hospitalization& $\sim normal(7.5, 1)$ & Davies et al.\\ 
     $d_{ICU}$ & Duration from hospitalization to ICU& $\sim normal(3.6, 1)$ & Davies et al.\\ 
     $d_{R,hosp}$ & Average stay in hospital & $\sim normal(11.08, 1.2)$ & Davies et al.\\ 
     $d_{R,ICU}$ & Average stay in hospital & $\sim normal(13.33, 1.2)$ & Davies et al.
    \end{tabular}
\end{table}
\end{center}
